Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-06 paper/paper-nature-revised.tex
lindsay updates

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Digitization of the Australian Parliamentary Debates, 1998-2022},
  pdfauthor={Lindsay Katz; Rohan Alexander},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, enhanced, interior hidden, frame hidden, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, \textbf{formally
known as Hansard\textsuperscript{1},} plays a fundamental role in
capturing the history of political proceedings and facilitating the
exploration of valuable research questions. Originating in the British
parliament, the production of Hansard became tradition in many other
Commonwealth countries, such as Canada and Australia\textsuperscript{2}.
Given the content and magnitude of these records, they have
significance, particularly in the context of political science research.
In the case of Canada, the Hansard has been digitized for 1901 to
2019\textsuperscript{3}. Having a digitized version of Hansard enables
researchers to conduct text analysis and statistical modelling.
Following the lead of that project, in this paper we introduce a similar
database for Australia. This is composed of individual datasets for each
sitting day in the House of Representatives from 1998 to 2022,
containing details on everything said in parliament in a form that can
be readily used by researchers. With the development of tools for
large-scale text analysis, this database will serve as a resource for
understanding political behaviour in Australia over time.

\textbf{There are a wide variety of potential applications of this
database. For instance, within Australia there is considerable concern
that there has been a decline in the `quality' of public policy debate
(however that might be defined). Our dataset could be used to look at
whether it is really getting worse in particular ways, and if so, why.
We might also be interested in whether particular sub-populations are
appropriately represented in what is talked about in parliament. For
instance, there is often concern that regional areas are overlooked
compared with metropolitan areas. Again, our database could be used to
examine whether this has changed over time. We have developed our
database in such a way that it could be linked with similar databases
from other countries which would enable comparative analysis. For
instance, we may be interested in how the policy focus of a parliament
changes given various global events such as pandemics or wars. An
international linkage provides a comparison case where domestic issues
are different while international ones are common. As an example of
enabling this linkage this we have included partyfacts IDs in our
database. This should make it possible to link our database with other
large parliamentary speech collection projects, such as
ParlaMint\textsuperscript{4}, ParlSpeech\textsuperscript{5},
ParlEE\textsuperscript{6}, and MAPLE\textsuperscript{7}.}

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not easily accessible for large scale analysis. To
this point, various researchers have had to create their own databases
of usable, complete data based on content from the Australian Parliament
website. For instance, an online, easy to read database of Hansard from
1901 to 1980 using the XML files has been created\textsuperscript{9}.
These data can be navigated by year, parliament, people, and
bills\textsuperscript{9}. To make the Australian Parliamentary Handbook
more accessible, an \texttt{R} package which includes data on all MPs
from 1945 to 2019 has been created\textsuperscript{10}. Further, there
is the \texttt{AustralianPoliticians} \texttt{R} package, which contains
several datasets related to the political and biographical information
of Australian federal politicians who were active between 1901 and
2021\textsuperscript{11}. \textbf{And finally, there has been
examination of speech and MP level data between 1990 and 2019 in
Australia\textsuperscript{12}. Like us they scrape the Hansard record
and link it with biographical data. They key difference is that our
focus is on the database itself, while are focused on using a database
constructed from the same source to answer a particular question about
speaker time. This different focus leads to different emphasis and
approaches.}

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, the Hansard has been used to
investigate occurrences of unparliamentary comments by MPs, where the
Speaker tells that MP to withdraw their remark\textsuperscript{13}.
Question Time data from Hansard transcripts during February and March of
2003 has been used to investigate resistance of politicians in answering
questions about Iraq\textsuperscript{14}. Hansard has been used to
quantify political prominence by investigating strategic mentions of
interest groups by elected officials\textsuperscript{15}. Finally, a
dataset of the Australian Hansard has been constructed and then used to
analyze the effect of elections and changes in Prime Ministers upon
topics mentioned in parliament\textsuperscript{16}. This was created
with the static PDF versions of Hansard, using OCR to digitize these
files into text which is suitable for analysis. This means there are
considerable digitization errors especially in the first half of the
dataset.

@@

\begin{quote}
\end{quote}

@@

When building our first scripts, one of the final components needed was
to separate general stage directions out from statements made by MPs.
Stage directions are general statements included in the transcript to
document happenings in parliament. Examples of stage directions are
``Bill read a second time'', ``Question agreed to'', or ``Debate
adjourned''. It was unclear to us from the XML and PDF who exactly these
statements were attributed to. For further clarification, we watched
portions of the video recording for some sitting days, and noticed that
while these statements are documented in Hansard, they are not
explicitly stated in parliament. For example, when the Deputy Speaker
says ``The question is that the bill be now read a second time'', MPs
vote, and if the majority is in favour, they proceed reading the bill
the second time. This vote and second reading is not explicitly
transcribed, rather what is written is: ``Question agreed to. Bill read
a second time''. For this reason, we filled the name variable for these
statements with ``stage direction''. Stage directions were not flagged
as interjections. These stage directions are not defined differently
from the regular debate speech in the XML, meaning we had to manually
create a list of stage directions to separate out of the speeches. We
built this list of stage directions as we worked backwards in parsing
Hansard, and took the same approach across all four scripts.
\textbf{Despite our best efforts to capture all stage directions in this
list, because it had to be built manually, users should be aware that it
is possible that some stage directions were not separated onto their own
rows in the process. Further, it is important to note that because they
are not spoken aloud, stage directions do not represent speech
components in the same way that all other components such as
interjections and continuations do. However, they provide valuable
information about the inner-workings and structure of parliamentary
events.}

@@

\textbf{To enhance the range of research questions which can be explored
with our data, we have created a supplementary file containing debate
topics and their corresponding page numbers for each sitting day in our
database. To extract these data, we wrote a script to parse debate and
sub-debate 1 information elements from each XML file in chronological
order using the XPath expression
``\texttt{//debate/debateinfo\ \textbar{}\ //subdebate.1/subdebateinfo}'',
and added a date variable with the date of each sitting day. Note that
in some cases there were multiple page number child nodes for the same
debate or sub-debate title, likely due to manual transcription error.
Upon manual inspection, we found that most often, the second page number
node contained the same page number as the first node, and sometimes the
second node contained a repeated debate title or a time stamp.
Therefore, we took the first available page number child-node for each
debate or sub-debate node to be the one we included in our dataset.}

@@

\textbf{In the Hansard XML files, divisions data are structured outside
of the \texttt{\textless{}speech\textgreater{}} content in their own
\texttt{\textless{}division\textgreater{}} nodes that contain the voting
data and division result. Since we focus primarily on the spoken
\texttt{\textless{}speech\textgreater{}} Hansard content, our parsing
scripts do not necessarily capture all divisions data from House
proceedings. Our approach to parsing Hansard in the third and fourth
scripts described in Section~\ref{sec-diff} naturally allowed for much
of the divisions data to be added to our resulting files for 1998 to
March 2011, however the parsing scripts used for May 2011 to September
2022 Hansard did not. To supplement our database and in an effort to
fill this divisions data gap, we created an additional file containing
all divisions data nested under the XPath
``\texttt{//chamber.xscript//division}'' from the Hansard files in our
time frame. To produce this data file, for each Hansard XML we parsed
the \texttt{\textless{}division.header\textgreater{}},
\texttt{\textless{}division.data\textgreater{}}, and
\texttt{\textless{}division.result\textgreater{}} child-nodes where they
existed, extracted any time stamps where available, and did any
additional data cleaning as necessary. We used a series of if-else
statements in this script to account for variation in the structure of
the \texttt{\textless{}divisions\textgreater{}} node over time. Finally,
we then added a date variable to distinguish between sitting days.}

@@

Our database is available in both CSV and parquet formats. Both CSV and
parquet are open standards. We provide both because while CSVs are
commonly used and can be manually inspected, parquet files are typically
smaller and preserve class. Our database covers all sitting days of the
House of Representatives from 02 March 1998 to 08 September 2022
\textbf{where an XML transcript is available}, so there are
\textbf{1,532 individual sitting day} files for each format.
\textbf{Additionally, there is a single corpus file in both CSV and
Parquet forms containing the data from all sitting days, with a date
variable added to allow for distinction and filtering of individual
sitting days. There is also a CSV and Parquet file containing all parsed
debate topics.} All data records are available on the general-purpose
repository Zenodo, at
https://doi.org/10.5281/zenodo.7799678\textsuperscript{21}. For each
\textbf{Hansard data} file, \textbf{that is, the corpus and the
individual sitting day files}, each row contains an individual
statement, with details on the individual speaking. For general
statements transcribed as made by ``Honourable members'' for example,
these variables cannot be specified. Table~\ref{tbl-vars} provides an
overview of each variable found in the \textbf{Hansard data files in
the} database.

@@

\textbf{As mentioned, in addition to the Hansard data described above,
our database also contains a CSV and Parquet file with the parsed debate
topics. This file is called \texttt{all\_debate\_topics}, and contains a
\texttt{date} variable specifying the sitting day, an
\texttt{item\_index} variable to specify the order of proceedings
(i.e.~the order in which these topics were discussed), a \texttt{title}
variable containing the debate or sub-debate title contents, and a
\texttt{page.no} variable specifying on which page that title was
recorded to be found in the official Hansard PDF.}

@@

\textbf{Finally, our database contains a file with all parsed divisions
data in our timeframe. This is called \texttt{division\_data}, and is
available in RDA form and in Parquet form. The reason it is not
available in CSV form is because three of the variables
(\texttt{names\_AYES}, \texttt{names\_NOES}, and \texttt{names\_PAIRS})
are lists, which are not supported by the CSV rectangular data
structure. The variables found in these data are summarized below, in
Table~\ref{tbl-divisions}.}

@@

\textbf{We then computed the total number of speeches made in our
database by political party, summarized in
Table~\ref{tbl-speeches_by_party}. We found that the Australian Labor
Party made the most speeches overall, followed by the Liberal Party of
Australia, and the Nationalist Party. These rankings are unsurprising,
as those parties are the three main political parties in the Australian
House of Representatives\textsuperscript{22}.}

@@

\textbf{Finally, the README file on our GitHub repository and on Zenodo
contains example code on how to read in a file from our database, for
both CSV and Parquet formats. Should a user wish to use the single
Hansard corpus rather than individual sitting day files, we provide
example code on how to read it in, filter for those sitting days of
interest, and split them into distinct data frames. We have also added
example code for filtering out stage directions, and updating the
\texttt{order} variable to reflect the ordering of remaining rows,
should the user wish to remove stage directions from their analysis.
Lastly, the README contains example code showing users how to merge the
debate topics data with a Hansard data file for one sitting day.}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Leslie_2021_HoR_Aus}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Leslie, P.
\href{https://github.com/palesl/AustralianHouseOfRepresentatives}{Members
of the australian house of representatives (1945-2019)}. (2021).}

@@

\leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{Katz, L. \& Alexander, R. {A new, comprehensive database
of all proceedings of the Australian Parliamentary Debates (1998-2022)}.
(2023)
doi:\href{https://doi.org/10.5281/zenodo.7799678}{10.5281/zenodo.7799678}.}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Digitization of the Australian Parliamentary Debates, 1998-2022},
  pdfauthor={Lindsay Katz; Rohan Alexander},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

The official written record of parliamentary debates, \textbf{formally
known as Hansard\textsuperscript{1},} plays a fundamental role in
capturing the history of political proceedings and facilitating the
exploration of valuable research questions. Originating in the British
parliament, the production of Hansard became tradition in many other
Commonwealth countries, such as Canada and Australia\textsuperscript{2}.
Given the content and magnitude of these records, they have
significance, particularly in the context of political science research.
In the case of Canada, the Hansard has been digitized for 1901 to
2019\textsuperscript{3}. Having a digitized version of Hansard enables
researchers to conduct text analysis and statistical modelling.
Following the lead of that project, in this paper we introduce a similar
database for Australia. This is composed of individual datasets for each
sitting day in the House of Representatives from 1998 to
\textbf{September} 2022, containing details on everything said in
parliament in a form that can be readily used by researchers. With the
development of tools for large-scale text analysis, this database will
serve as a resource for understanding political behaviour in Australia
over time.

\textbf{There are a wide variety of potential applications of this
database. For instance, within Australia there is considerable concern
that there has been a decline in the `quality' of public policy debate
(however that might be defined). Our dataset could be used to look at
whether it is really getting worse in particular ways, and if so, why.
We might also be interested in whether particular sub-populations are
appropriately represented in what is talked about in parliament. For
instance, there is often concern that regional areas are overlooked
compared with metropolitan areas. Again, our database could be used to
examine whether this has changed over time. We have developed our
database in such a way that it could be linked with similar databases
from other countries which would enable comparative analysis. For
instance, we may be interested in how the policy focus of a parliament
changes given various global events such as pandemics or wars. An
international linkage provides a comparison case where domestic issues
are different while international ones are common. As an example of
enabling this linkage we have included PartyFacts IDs in our database.
This should make it possible to link our database with other large
parliamentary speech collection projects, such as
ParlaMint\textsuperscript{4}, ParlSpeech\textsuperscript{5},
ParlEE\textsuperscript{6}, and MAPLE\textsuperscript{7}.}

@@

At present, the Hansard format that is available on the Parliament of
Australia website is not easily accessible for large scale analysis. To
this point, various researchers have had to create their own databases
of usable, complete data based on content from the Australian Parliament
website. For instance, an online, easy to read database of Hansard from
1901 to 1980 using the XML files has been created\textsuperscript{9}.
These data can be navigated by year, parliament, people, and
bills\textsuperscript{9}. To make the Australian Parliamentary Handbook
more accessible, an \texttt{R} package which includes data on all MPs
from 1945 to 2019 has been created\textsuperscript{10}. Further, there
is the \texttt{AustralianPoliticians} \texttt{R} package, which contains
several datasets related to the political and biographical information
of Australian federal politicians who were active between 1901 and
2021\textsuperscript{11}. \textbf{And finally, there has been
examination of speech and MP level data between 1990 and 2019 in
Australia\textsuperscript{12}. Like us they scrape the Hansard record
and link it with biographical data. The key difference is that our focus
is on the database itself, while they are focused on using a database
constructed from the same source to answer a particular question about
speaker time. This different focus leads to different emphasis and
approaches.}

Many papers exist which use components of Australian Hansard to explore
various research topics. For example, the Hansard has been used to
investigate occurrences of unparliamentary comments by MPs, where the
Speaker tells that MP to withdraw their remark\textsuperscript{13}.
Question Time data from Hansard transcripts during February and March of
2003 has been used to investigate resistance of politicians in answering
questions about Iraq\textsuperscript{14}. Hansard has also been used to
quantify political prominence by investigating strategic mentions of
interest groups by elected officials\textsuperscript{15}. Finally, a
dataset of the Australian Hansard has been constructed and then used to
analyze the effect of elections and changes in Prime Ministers upon
topics mentioned in parliament\textsuperscript{16}. This was created
with the static PDF versions of Hansard, using OCR to digitize these
files into text which is suitable for analysis. This means there are
considerable digitization errors especially in the first half of the
dataset.

@@

@@

When building our first scripts, one of the final components needed was
to separate general stage directions out from statements made by MPs.
Stage directions are general statements included in the transcript to
document happenings in parliament. Examples of stage directions are
``Bill read a second time'', ``Question agreed to'', or ``Debate
adjourned''. It was unclear to us from the XML and PDF who exactly these
statements were attributed to. For further clarification, we watched
portions of the video recording for some sitting days, and noticed that
while these statements are documented in Hansard, they are not
explicitly stated in parliament. For example, when the Deputy Speaker
says ``The question is that the bill be now read a second time'', MPs
vote, and if the majority is in favour, they proceed reading the bill
the second time. This vote and second reading is not explicitly
transcribed, rather what is written is: ``Question agreed to. Bill read
a second time''. For this reason, we filled the name variable for these
statements with ``stage direction''. Stage directions were not flagged
as interjections. These stage directions are not defined differently
from the regular debate speech in the XML, meaning we had to manually
create a list of stage directions to separate out of the speeches. We
built this list of stage directions as we worked backwards in parsing
Hansard, and took the same approach across all four scripts.
\textbf{Despite our best efforts to capture all stage directions in this
list, because it had to be built manually, users should be aware that it
is possible that some stage directions were not separated onto their own
rows in the process. Further, it is important to note that because they
are not spoken aloud, stage directions do not represent speech
components in the same way that all other components such as
interjections and continuations do. However, they provide valuable
information about the inner-workings and structure of parliamentary
events. If the focus on the user's research does not require stage
directions, then this can be removed by filtering observations in name
equal to ``business start'', or ``stage direction''.}

@@

\textbf{To enhance the range of research questions which can be explored
with our data, we have created a supplementary file containing debate
topics and their corresponding page numbers for each sitting day in our
database. To extract these data, we wrote a script to parse debate and
sub-debate 1 information elements from each XML file in chronological
order using the XPath expression
``\texttt{//debate/debateinfo\ \textbar{}\ //subdebate.1/subdebateinfo}'',
and added a date variable with the date of each sitting day. Note that
in some cases there were multiple page number child nodes for the same
debate or sub-debate title, likely due to manual transcription error.
Upon manual inspection, we found that most often, the second page number
node contained the same page number as the first node, and sometimes the
second node contained a repeated debate title or a time stamp.
Therefore, we took the first available page number child-node for each
debate or sub-debate node to be the one we included in our dataset.
After summarizing, these topics can be added to the main text by
joining, and example code is provided in the README.}

@@

\textbf{In the Hansard XML files, divisions data are structured outside
of the \texttt{\textless{}speech\textgreater{}} content in their own
\texttt{\textless{}division\textgreater{}} nodes that contain the voting
data and division result. Since we focus primarily on the spoken
\texttt{\textless{}speech\textgreater{}} Hansard content, our parsing
scripts do not necessarily capture all divisions data from House
proceedings. Our approach to parsing Hansard in the third and fourth
scripts described in Section~\ref{sec-diff} naturally allowed for much
of the divisions data to be added to our resulting files for 1998 to
March 2011, however the parsing scripts used for May 2011 to September
2022 Hansard did not. To supplement our database and in an effort to
fill this divisions data gap, we created an additional file containing
all divisions data nested under the XPath
``\texttt{//chamber.xscript//division}'' from the Hansard files in our
time frame. To produce this data file, for each Hansard XML we parsed
the \texttt{\textless{}division.header\textgreater{}},
\texttt{\textless{}division.data\textgreater{}}, and
\texttt{\textless{}division.result\textgreater{}} child-nodes where they
existed, extracted any time stamps where available, and did any
additional data cleaning as necessary. We used a series of if-else
statements in this script to account for variation in the structure of
the \texttt{\textless{}division\textgreater{}} node over time. Finally,
we then added a date variable to distinguish between sitting days.}

@@

Our database is available in both CSV and parquet formats. \textbf{Both
CSV and parquet are open standards. We provide both because while CSVs
are commonly used and can be manually inspected, parquet files are
typically smaller and preserve class.} Our database covers all sitting
days of the House of Representatives from 02 March 1998 to 08 September
2022 \textbf{where an XML transcript is available}, so there are
\textbf{1,532 individual sitting day} files for each format.
\textbf{Additionally, there is a single corpus file in both CSV and
parquet forms containing the data from all sitting days, with a date
variable added to allow for distinction and filtering of individual
sitting days. There is also a CSV and parquet file containing all parsed
debate topics.} All data records are available on the general-purpose
repository Zenodo, at
\url{https://doi.org/10.5281/zenodo.7336075}\textsuperscript{21}. For
each \textbf{Hansard data} file, \textbf{that is, the corpus and the
individual sitting day files}, each row contains an individual
statement, with details on the individual speaking. For general
statements transcribed as made by ``Honourable members'' for example,
these variables cannot be specified. Table~\ref{tbl-vars} provides an
overview of each variable found in the \textbf{Hansard data files in
the} database.

@@

\textbf{As mentioned, in addition to the Hansard data described above,
our database also contains a CSV and parquet file with the parsed debate
topics. This file is called \texttt{all\_debate\_topics}, and contains a
\texttt{date} variable specifying the sitting day, an
\texttt{item\_index} variable to specify the order of proceedings
(i.e.~the order in which these topics were discussed), a \texttt{title}
variable containing the debate or sub-debate title contents, and a
\texttt{page.no} variable specifying on which page that title was
recorded to be found in the official Hansard PDF.}

@@

\textbf{Finally, our database contains a file with all parsed divisions
data in our timeframe. This is called \texttt{division\_data}, and is
available in RDA form and in parquet form. The reason it is not
available in CSV form is because three of the variables
(\texttt{names\_AYES}, \texttt{names\_NOES}, and \texttt{names\_PAIRS})
are lists, which are not supported by the CSV rectangular data
structure. The variables found in these data are summarized below, in
Table~\ref{tbl-divisions}.}

@@

\textbf{We then computed the total number of speeches made in our
database by political party, summarized in
Table~\ref{tbl-speeches_by_party}. We found that the Australian Labor
Party made the most speeches overall, followed by the Liberal Party of
Australia, and the National Party of Australia. These rankings are
unsurprising, as those parties are the three main political parties in
the Australian House of Representatives\textsuperscript{22}.}

@@

\textbf{Finally, the README file on our GitHub repository and on Zenodo
contains example code on how to read in a file from our database, for
both CSV and parquet formats. Should a user wish to use the single
Hansard corpus rather than individual sitting day files, we provide
example code on how to read it in, filter for those sitting days of
interest, and split them into distinct data frames. We have also added
example code for filtering out stage directions, and updating the
\texttt{order} variable to reflect the ordering of remaining rows,
should the user wish to remove stage directions from their analysis.
Lastly, the README contains example code showing users how to merge the
debate topics data with a Hansard data file for one sitting day.}

@@

\leavevmode\vadjust pre{\hypertarget{ref-Leslie_2021_HoR_Aus}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Leslie, P.
\emph{\href{https://github.com/palesl/AustralianHouseOfRepresentatives}{Members
of the australian house of representatives (1945-2019)}}. (2021).}

@@

\leavevmode\vadjust pre{\hypertarget{ref-katz_2023}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{Katz, L. \& Alexander, R. {A new, comprehensive database
of all proceedings of the Australian Parliamentary Debates (1998-2022)}.
(2023)
doi:\href{https://doi.org/10.5281/zenodo.7336075}{10.5281/zenodo.7336075}.}
